Market-based Mechanisms for Resource Scheduling

### 2013-12-17 paper/paper.tex
Write more about auction

@@

\section{Market-based Mechanism Design}
\label{sec:design}

>>>>

\usepackage{mathtools}
\usepackage{graphicx}

@@

\section{Market-based Mechanism Design}
\label{sec:design}
\subsection{Setting}
Our mechanism assumes three types of participants: a single \emph{master} for
the cluster which manages a large number of \emph{slaves} serving as a pool of
compute resources. The users of the system are represented by \emph{frameworks},
which communicate with the master to request resources on slaves, and use the
obtained resources to run \emph{tasks} on the slaves.

These participants generally run as daemons on the cluster.  Typically, a single
cluster would consist of up to tens of thousands of machines, each of which
running a slave process. A single master process (or multiple redundant ones
for reliability) communicates directly with all slave processes.  Each slave
process manages the tasks which run on its machine, handling requests to start
and stop various tasks from the master.

The frameworks representing the clusters also run as daemons and register
themselves with the master. They communicate exclusively with the master, which
mediates all needed communication with the slaves, such as details on the task
to be run.

\subsection{Budgets and income}
The master keeps track of a budget for each framework: its current balance and
the amount of income it receives per second. The automatically adjusts a
framework's balance when it performs actions which require payment. Currently,
we allow a framework to incur a negative income (if it is spending beyond its
means) and also a negative balance (if negative income lasts long enough to
remove all of the savings) for simplicity.

\subsection{Resource offers and bidding}
Periodically, when there are resources currently available, the master will
send a \emph{resource offer} message to all registered frameworks to invite them
to participate in an upcoming auction. Each framework then submits a package of
bids, which we can consider a function of the form
\[ \mathcal{B}: \mathbf{T}^n \rightarrow \mathbf{R}. \]
where there are $n$ slaves, $T$ is a task (containing an amount of desired
resources on a single slave) and $\mathbf{R}$ is a willingness to pay for the
list of tasks $\mathbf{T}^n$.

A naive representation of this function would use an exponential amount of
space, given that each of the $n$ values in $\mathbf{T}^n$ can vary
independently. While we can consider several methods for restricting the set of
possible
